Constructing a universe for the setoid model

### 2020-01-09 types20-abstract.tex
added titlerunning and authorrunning
added blank before Kaposi

\title{Constructing a universe for the setoid model}

\author{Thorsten Altenkirch\inst{1}\thanks{Supported by USAF grant
    FA9550-16-1-0029.} \and AmbrusKaposi \inst{2} \and Filippo Sestini\inst{1}}

>>>>

\title{Constructing a universe for the setoid model}
\titlerunning{Constructing a universe for the setoid model}
\authorrunning{Altenkirch, Kaposi, Sestini}

\author{Thorsten Altenkirch\inst{1}\thanks{Supported by USAF grant
    FA9550-16-1-0029.} \and Ambrus Kaposi \inst{2} \and Filippo Sestini\inst{1}}
